{\sl Thesis: Temporal \textsc{NetKAT}}, \hfill  Aug 2016 - Present \\
Pomona College, Advisor: Michael Greenberg
\begin{itemize} \itemsep -2pt
  \item Develop an equational theory for $LTL_f$, a finite variant of LTL
  \item Prove Soundness and Completeness for Temporal \textsc{NetKat} with its
    denotational semantics over $LTL$.
\end{itemize}

{\sl Temporal Pattern Matching}, \hfill June 2016 - Aug 2016 \\
Pomona College, Advisor: Melanie Wu
\begin{itemize} \itemsep -2pt
  \item Developed temporal semantics for queries of graph data (e.g. social networks).
  \item Extended most performant algorithm with temporal verification techiques.
  \item Implemented the algorithm in C++ with tenfold efficiency improvements.
  \item To be submitted for publication
\end{itemize}

{\sl Constructing Integer Matrices with Integer Eigenvalues}, \hfill Sept 2015 - Jan 2016\\
\textbf{Published}: \textit{The Mathematical Scientist}. Jun 2016, Vol. 41 Issue 1, p45-52. 8p. \\
Scripps College, Advisor: Christopher Towse
\begin{itemize} \itemsep -2pt
  \item Developed a matrix-generation application that outputs an integer matrix
    with integer Eigenvalues given an arbitrary integer matrix
\end{itemize}


{\sl Temporal Path Queries}, \hfill Jan 2016 - May 2016 \\
Pomona College, Advisor: Melanie Wu
\begin{itemize} \itemsep -2pt
  \item Theorized many algorithmic approaches to various definitions of temporal paths.
  \item Implemented several of these algorithms in Python and MySQL, determining
    MySQL's utter inefficacy at dealing with graph data.
\end{itemize}

{\sl GitHub Pilot Study}, \hfill Aug 2015 - Dec 2015 \\
Pomona College, Advisor: Tzu-Yi Chen
\begin{itemize}\itemsep -2pt
  \item Developed GitHub distribution-submission-grading architecture for Intro CS course.
  \item Studied impact on student learning and course overhead.
\end{itemize}
